Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-02 GECCO/volunteer-clouds-gecco16.tex
Comments at the end of the introduction

In this paper, we will carry out three experiments, after establishing
the baseline of the performance that can be expected in a JavaScript
based system and its comparison with other languages in
\cite{2016arXiv160101607Manom}. First, several experiments using a
Platform as a Service, and a simple Ajax client that does not
restart. Second, we change a bit the client so that it uses web
workers, that is, it runs in the background and it restarts. Third, we use the same
client, but with a harder problem that cannot be solved by a single
volunteer and thus needs the contribution of many volunteers to
proceed. With these three experiments we want mainly to try and model
the behavior of users and how different problems and implementations
have an influence on it.

So, the rest of the paper is organized as follows: Next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. A brief presentation of the
methodology used and the results of the experiments are presented in
Section \ref{sec:exp1}, including new results using web workers on the
same problem and on a new problem, Rastrigin's or F15 function. 
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

>>>>

In this paper, we will carry out three experiments, after establishing
the baseline of the performance that can be expected in a JavaScript
based system and its comparison with other languages in
\cite{2016arXiv160101607Manom}. First, several experiments using a
Platform as a Service, and a simple Ajax client that does not
restart. Second, we change a bit the client so that it uses web
workers, that is, it runs in the background and it restarts. Third, we use the same
% Pablo: it restarts when the solution is found (it has not been mentioned yet)
client, but with a harder problem that cannot be solved by a single
volunteer and thus needs the contribution of many volunteers to
proceed. With these three experiments we want mainly to try and model
the behavior of users and how different problems and implementations
have an influence on it. 
%Pablo: To do this we compare the time spent by each user because...

So, the rest of the paper is organized as follows: next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. A brief presentation of the
methodology used and the results of the experiments are presented in
%Pablo: mention the problems used in the first experiments
Section \ref{sec:exp1}, including new results using web workers on the
same problem and on a new problem, Rastrigin or F15 function. 
%Pablo: Rastrigin is not the owner of the function
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.
